---
title: "Find_Duplicates"
author: "Valerie Gartner"
date: "10/6/2020"
output: html_document
---

NOTE: NEXT TIME I NEED TO DO THIS, JUST USE THE FUNCTION distinct() !!!!!!!
https://www.datanovia.com/en/lessons/identify-and-remove-duplicate-data-in-r/



```{r}
suppressMessages(library(dplyr))
suppressMessages(library(tidyverse))
```

```{r}
sample_table <- as.data.frame(read.csv('~/Dropbox (Duke Bio_Ea)/coalescent/samples/tables/merged-sample-table.csv', na.strings=c("", "NA")))

#full table
#sample_table

#duplicate accession numbers
dups <- sample_table[duplicated(sample_table$accession),]

setwd('~/Dropbox (Duke Bio_Ea)/scripts/r-scripts/')
write.table(dups, "duplicate_accessions.txt", sep=",",col.names=TRUE,row.names=FALSE,quote=FALSE)
```


Look at the full table and see if there are any duplicates by sample_ID field		
```{r}
#pull out only samples with a sample ID
samp_ID <- dups %>% drop_na(sample_ID)
#samp_ID

#duplicate accession numbers
dup_sampID <- samp_ID[duplicated(samp_ID$sample_ID),]
#dup_sampID #no duplicates


smpdups <- sample_table[duplicated(sample_table$sample_ID),] %>% drop_na(sample_ID)
smpdups


```

It appears there are some duplicate sample IDs...?

Why are some sample IDs from the same study listed with different accession numbers?
e.g.
ERS403525		Malaysia	1157	PY0019-C #ERS is the sample number
ERR527363		Malaysia	1157	PY0019-C


Can I delete all samples that start with ERS because they're already present in the database in ERR form?
```{r}
#split samp_Id into two dataframes - one with only ERS and the other withonly ERR
#library(stringr)
#couldn't figure out how to do this in R. gonna export and do in python.


samp_acc <- select(samp_ID, "accession", "sample_ID")
#samp_acc
#use sample_IDs as the key to pull out all rows that match the sample ID

#duped_sampID <- sample_table[sample_table$sample_ID %in% samp_acc$sample_ID]
duped_sampID <- filter(sample_table, sample_ID %in% samp_acc$sample_ID)
duped_sampID <- select(duped_sampID, "accession", "sample_ID")
#https://stackoverflow.com/questions/11612235/select-rows-from-a-data-frame-based-on-values-in-a-vector
# "try: dt[dt$fct %in% vc,] Basically == is for one item and %in% is for a vector comparison."

#setwd('~/Dropbox (Duke Bio_Ea)/coalescent/samples/tables/')
#write.table(duped_sampID, "sample_ID_accessions.csv", sep=",",col.names=FALSE,row.names=FALSE,quote=FALSE)
# ended up doing this bit in python ~/scripts/python/split-sampleIDs-compare.py
# output of that script is imported in the next chunk

```

```{r}
ers_to_delete <- as.data.frame(read.csv('~/Dropbox (Duke Bio_Ea)/scripts/python-scripts/ERS-to-delete.txt'))
#ers_to_delete


#remove samples beginning with ERS
final_table_noers <- filter(sample_table, !accession %in% ers_to_delete$x)
#final_table[order(final_table$accession),]
                      
                
#final_table_noers
final_table_distinct <- distinct(final_table_noers, accession, .keep_all=TRUE) # I should have used this function the whole time -_-
#final_table_sorted
#final_table_sorted[order(final_table_sorted$country),]

setwd('~/Dropbox (Duke Bio_Ea)/coalescent/samples/tables/')
write.table(final_table_distinct, "merged-sample-table-noduplicates.csv", sep=",",col.names=TRUE,row.names=FALSE,quote=FALSE)
write.table(final_table_distinct$accession, "accesions-merged-sample-table-noduplicates.txt", col.names=FALSE,row.names=FALSE,quote=FALSE)
```


```{r}
test <- data.frame(c('scooby', 'dooby', 'dooby', 'do', 'where', 'are', 'you'), c(1, 2, 3, 4, 5, 6, 7))
test
test <- test %>% distinct(c..scooby....dooby....dooby....do....where....are....you.., .keep_all = TRUE)
test
```