---
title: "SRR_cleanup"
author: "Valerie Gartner"
date: "10/20/2020"
output: html_document
---

```{r}
suppressMessages(library(dplyr))
suppressMessages(library(tidyverse))
```

```{r}
xfer_list <- as.data.frame(read.csv("/Users/vgartner/Desktop/2020.10.20-SRR-organization/xfer-SRR.csv")) #284 cols
hardac_dirs <- as.data.frame(read.csv("/Users/vgartner/Desktop/2020.10.20-SRR-organization/hardac-SRR-dirs.csv")) #313 cols #29 cols diff

xfer_list
hardac_dirs

```


find the 29 unique accessions and write to file
```{r}

unique_list <- filter(hardac_dirs, !acc %in% xfer_list$acc)
unique_list

setwd('/Users/vgartner/Desktop/2020.10.20-SRR-organization/')
#write.table(unique_list, "29-samps-to-scp.txt", sep="",col.names=FALSE,row.names=FALSE,quote=FALSE)

```



I sorted through the sample directories moved to wraycompute2 via xfer node to get the following lists:
```{r}
full_list <- as.data.frame(read.csv("/Users/vgartner/Desktop/2020.10.20-SRR-organization/accesions-merged-sample-table-noduplicates.csv")) #994 cols
to_rerun_list <- as.data.frame(read.csv("/Users/vgartner/Desktop/2020.10.20-SRR-organization/samps-to-rerun.csv")) #268 cols
done_list <- as.data.frame(read.csv("/Users/vgartner/Desktop/2020.10.20-SRR-organization/samps-gvcf-done.csv")) #208 cols

# 518 samples haven't been run yet
# total to-run list should have 786 columns
#

#full_list
#to_rerun_list
#done_list
```
There are 994 total accessions I want to get gvcfs for.
So far I have successfuly gotten 208 samples processed.
268 samples started a run but didn't finish
518 samples haven't been run yet...

...so the total number I need to run next round is 786.
I think I'll put them in lists of ~200 so I can check on the progress and move to /nfs/wraycompute2/val/gvcf/ as needed


Find the 786 accessions I still need to run
```{r}
full_list
samps_to_run <- filter(full_list, !acc %in% done_list$acc)
samps_to_run
setwd('/Users/vgartner/Desktop/2020.10.20-SRR-organization/')
write.table(samps_to_run, "acc-to-run.txt", sep="",col.names=FALSE,row.names=FALSE,quote=FALSE)

#for future reference, probably not necessary
samps_never_run <- filter(samps_to_run, !acc %in% to_rerun_list$acc)
samps_never_run

```